### 2024-04-16 docs/SOSP 2024/schedule.tex
Edit scheduling lang section

>>>>

\Treebeard{} represents loops (index variables) as nodes in a tree where the children
of a node represent immediately contained loops. Each schedule 
primitive modifies this tree in some way. The compiler tracks 
the lineage of each of the loops. This allows the compiler to 
automatically infer the ranges for all loops.
